---
title: "Duckweeds, microbes, and symbiosis"
date: "Meeting program as of `r format(Sys.time(), '%b %d, %Y')`"
output: github_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, dev='png'}
library(here)
#htmltools::img(src = knitr::image_uri(here("Slide1.jpg")), alt = 'logo')
```

### Meeting Location

The meeting will take place in the Sage Ideas Lounge at the University of British Columbia. The venue is located at [6331 Crescent Rd, Vancouver, BC V6T 1Z1](https://maps.app.goo.gl/3sk4jVPN4AtCY3NL6)


## Thursday, May 30, 2024

**8:30am Continental Breakfast**

**9:00am-9:15am Megan Frederickson | University of Toronto**

*Welcome and opening remarks*

### Symbiosis model systems: duckweeds, *Arabidopsis,* and *C. elegans*

**9:15am-9:40am Na Wei | Holden Arboretum**

*Environment and host genetics influence Lemna microbial biogeography*

**9:40am-10:05am Talia Karasov | University of Utah**

*Pseudomonas pathogen populations suppress one another with a repurposed phage*

**10:05am-10:30am Fan Zhang | Louisiana State University**

*High-throughput analysis of microbial influence on the soil nematode C. elegans*

**10:30am-11am Coffee and Discussion**

*Topic: Digging into mechanisms of symbiosis in model systems*

### Software and hardware for automated high-throughput experiments with duckweeds and other small organisms

**11:00am-11:25am Nadya Peek and Blair Subbaraman | University of Washington**

*Demonstrating Science Jubilee: open-source hardware for laboratory automation*

**11:25am-11:50am Takuji Usui | University of Toronto**

*Using machine learning for automated lineage tracking in duckweeds*

**11:50am-12:20pm Discussion**

*Topic: Overcoming hardware and software challenges in high-throughput systems*

**12:20pm-2:00pm Lunch** Lunch will be provided for all meeting participants at the Sage Ideas Lounge. 

### Lightning talks: latest findings and methods

**2:00pm-2:05pm Amanda Luzardo | University of Lethbridge**

*Minimal assay detects population-level senescence in the aquatic plant Lemna minor*

**2:05pm-2:10pm Megan Frederickson | University of Toronto**

*Getting the duckweed microbiome into culture*

**2:10pm-2:15pm Chris Carlson | University of Toronto**

*An urbanization gradient impacts the duckweed microbiome*

**2:15pm-2:20pm Jiaqi Tan | Louisiana State University**

*Separating the direct and indirect plant-mediated impacts of environmental changes on plant microbiomes*

**2:20pm-2:25pm Kevin Ricks | University of Toronto**

*Using single strains to model plant-microbe interactions*

**2:25pm-2:30pm Suzanne Chmilar | University of Lethbridge**

*Parental age affects offspring response to salt stress in Lemna minor*

**2:30pm-2:40pm Q&A with lightning talk speakers**

### Duckweeds as an eco-evo model system

**2:40pm-3:05pm Amy Angert | University of British Columbia**

*Duckweeds as a model system for studying eco-evo dynamics of range expansion*

**3:05pm-3:30pm Rob Laird | University of Lethbridge**

*Demography and senescence in duckweed*

**3:30pm-4:30pm Coffee and Discussion**

*Topic: Experimental evolution and co-evolution using duckweeds*

**4:30pm-4:45pm Megan Frederickson | University of Toronto**

*Closing remarks*

**5:30pm-ish Dinner**

We will head out to dinner in small groups to several Vancouver restaurants; all are welcome, and details will be provided at the meeting. 
